---
title: "Single-nuclei analysis of white adipose tissue : Old Samples report"
author: "Nathalie"
date: "8/3/2021"
output: html_document
---

```{r packages, include = FALSE}
library(Seurat)
library(ggplot2)
library(cowplot)
library(patchwork)
library(ggpubr)
library(viridis)
library(ggsci)
library('SingleR')
library('celldex')
library('SingleCellExperiment')
library(pheatmap)
library(scran)
library(stringr)
library(monocle3)
library(SeuratWrappers)
```

```{r function, include = FALSE}
get_earliest_principal_node <- function(cds, ident){
  cell_ids <- which(colData(cds)[, "ident"] == ident)
  
  closest_vertex <-
  cds@principal_graph_aux[["UMAP"]]$pr_graph_cell_proj_closest_vertex
  closest_vertex <- as.matrix(closest_vertex[colnames(cds), ])
  root_pr_nodes <-
  igraph::V(principal_graph(cds)[["UMAP"]])$name[as.numeric(names
  (which.max(table(closest_vertex[cell_ids,]))))]
  
  root_pr_nodes
}

Mrna_ref<-MouseRNAseqData()

Mim_ref<-ImmGenData()

```

```{r color palette, message=FALSE, warning=FALSE, paged.print=FALSE}
Cell_types= c("Mature adipocyte","Pre-adipocyte 1 (Tshz2)", "Macrophage", "Precursor (Dao)", "Mature adipocyte (acaca)", "Endothelial cell", "Muscle cell", "Neutrophil", "Natural killer", "Pre-adipocyte 2 (adamtsl1)", "Lymphocyte","Dendritic cell","Undefined")

mypal=c("#D04F55","#2194EC","#E8CA5D","#35A984","#D45E57","#7D6AC8","#3F826D","#CACF85","#E4A278","#7BB0A8","#8BA87C","#E28413","#ADC2C1")
Colours=data.frame(Cell_types,mypal)

```

- List of samples :
  - Alo : batch2, good quality (alo_71)
  - Alo2 : batch 3, medium quality (aly_69)
  - DRo : bacth 2 , good quality (dro_72)
  - DRo2 : batch 3, bad quality (dro2_07)

***  

## AL old (71)

```{r load alo_71,message=FALSE,warning=FALSE, echo = FALSE}
alo_71.data <- Read10X(data.dir = "/Users/njaure/Documents/Main_thesis_project/10X_full_experiment_10.20/comp_data_10.20/71_alo/A006200124_136871_S9_L00Solo.out/GeneFull/raw/")

alo_71 <- CreateSeuratObject(counts = alo_71.data, project = "al_old", min.cells = 10, min.features = 80)
alo_71@meta.data$batch <- "batch_2"
alo_71@meta.data$diet<- "AL"
alo_71@meta.data$age <- "Old"
alo_71
```

- 4462 features across 1220 samples after first filtering of taking features across minimum 10 cells, and cells minimum 80 features. 

### Quality assessment

```{r plot quality alo, echo = FALSE}
alo_71[["percent.rp"]] <- PercentageFeatureSet(alo_71, pattern = "^Rp")
alo_71[["percent.mt"]] <- PercentageFeatureSet(alo_71, pattern = "^mt-")
VlnPlot(alo_71, features = c("nFeature_RNA", "nCount_RNA","percent.mt","percent.rp"), ncol = 4)

```

```{r plot quality 2 alo,echo = FALSE}
FeatureScatter(alo_71, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

```

- no big abnormality detected, filtering on 50<x<220,mt<2, rp<1

```{r filtering2 alo, message=FALSE, warning=FALSE,echo = FALSE}
alo_71 <- subset(alo_71, subset = nFeature_RNA > 50 & nFeature_RNA < 500 & nCount_RNA < 1000 & percent.mt < 2 & percent.rp < 1)

```

- 4462 features across 1185 samples after second filtering. 

### Normalisation

```{r sctransform alo,message=FALSE, warning=FALSE}
# run sctransform
alo_71 <- SCTransform(alo_71, vars.to.regress = c("percent.mt","percent.rp"), verbose = FALSE)
alo_71
```


***

## AL old 2 (6)


```{r load alo2_06,message=FALSE,warning=FALSE, echo = FALSE}
alo2_06.data <- Read10X(data.dir = "/Users/njaure/Documents/Main_thesis_project/10X_full_experiment_10.20/comp_data_10.20/06_alo2/A006200124_137506_S11_L00Solo.out/GeneFull/raw/")
alo2_06 <- CreateSeuratObject(counts = alo2_06.data, project = "al_old_2", min.cells = 10, min.features = 80)
alo2_06@meta.data$batch <- "batch_3"
alo2_06@meta.data$diet<- "AL"
alo2_06@meta.data$age <- "Old"
alo2_06
```

- 3733 features across 1126 samples after first filtering of taking features across minimum 10 cells, and cells minimum 80 features. 

### Quality assessment

```{r plot quality alo2, message=FALSE,warning=FALSE, echo = FALSE}
alo2_06[["percent.rp"]] <- PercentageFeatureSet(alo2_06, pattern = "^Rp-")
alo2_06[["percent.mt"]] <- PercentageFeatureSet(alo2_06, pattern = "^mt-")
VlnPlot(alo2_06, features = c("nFeature_RNA", "nCount_RNA","percent.mt","percent.rp"), ncol = 4)
```

```{r plot quality 2 alo2,echo = FALSE}
FeatureScatter(alo2_06, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

```


```{r filtering2 alo2, message=FALSE, warning=FALSE}
alo2_06 <- subset(alo2_06, subset = nFeature_RNA > 50 & nFeature_RNA < 400 & nCount_RNA < 1000 & percent.mt < 1 & percent.rp < 1)

```

- 3733 features across 1107 samples after second filtering, removing cells with not enough features.

### Normalisation

```{r sctransform alo2,message=FALSE, warning=FALSE}
# run sctransform
alo2_06 <- SCTransform(alo2_06, vars.to.regress = c("percent.mt","percent.rp"), verbose = FALSE)
alo2_06
```

***
<br>
***

### Merging

```{r merging alo,message=FALSE, warning=FALSE, echo = FALSE}
alo_data<-list(alo_71,alo2_06)
alo_features <- SelectIntegrationFeatures(object.list = alo_data, nfeatures = 5000)
alo_list <- PrepSCTIntegration(object.list = alo_data, anchor.features = alo_features, 
    verbose = FALSE)
alo_anchors <- FindIntegrationAnchors(object.list = alo_list, normalization.method = "SCT", 
    anchor.features = alo_features)
alo_combined.sct <- IntegrateData(anchorset = alo_anchors, normalization.method = "SCT")

alo_combined.sct <- RunPCA(alo_combined.sct, verbose = FALSE)
alo_combined.sct <- RunUMAP(alo_combined.sct, reduction = "pca", dims = 1:30)
```

- 12910 features across 2292 samples after merging.

```{r}
dim(alo_combined.sct)
```


```{r umap plot alo, echo = FALSE}
p1<-DimPlot(alo_combined.sct, reduction = "umap", group.by = "orig.ident")
p1
```

### Clustering

```{r clustering alo, echo = FALSE}
alo_combined.sct <- FindNeighbors(alo_combined.sct, reduction = "pca", dims = 1:30)
alo_combined.sct <- FindClusters(alo_combined.sct, resolution = 0.6)
p3 <- DimPlot(alo_combined.sct, reduction = "umap")
plot_grid( p1,p3)
```

```{r umap per quality criteria alo, echo = FALSE}
FeaturePlot(alo_combined.sct,features = c("nFeature_RNA", "nCount_RNA","percent.mt","percent.rp"))
```

### Gene Markers


```{r}
alo_combined.sct
DefaultAssay(alo_combined.sct)<-"SCT"
dim(alo_combined.sct)
```

```{r topmarker alo, echo = FALSE, warning=FALSE, message=FALSE}
all.markers_alo=FindAllMarkers(alo_combined.sct,only.pos = TRUE, min.pct = 0.3, logfc.threshold = 0.2,min.cells.feature = 50,test.use = "t")

top_features_alo=vector()
temp=vector()
for ( i in 0:length(unique(all.markers_alo$cluster))){
  if (nrow(all.markers_alo[all.markers_alo$cluster==i,])>10 ){
     temp= all.markers_alo[all.markers_alo$cluster==i,"gene"][1]
      top_features_alo<-c(top_features_alo,temp)
  }else {
    temp= all.markers_alo[all.markers_alo$cluster==i,"gene"][1]
      top_features_alo<-c(top_features_alo,temp)
    
  }


}

VlnPlot(alo_combined.sct, features = top_features_alo, 
    pt.size = 0.2, stack=TRUE)


```



```{r feature plot alo, echo = FALSE, warning=FALSE}
FeaturePlot(alo_combined.sct, features = top_features_alo, pt.size = 0.2, 
    ncol = 3)
FeaturePlot(dro_combined.sct, features = c("Acaca","Acly"), pt.size = 0.2, 
    ncol = 3)
```


```{r heatmap alo, echo = FALSE, warning=FALSE, message=FALSE}

top_features_alo=vector()
temp=vector()
for ( i in 0:length(unique(all.markers_alo$cluster))){
  if (nrow(all.markers_alo[all.markers_alo$cluster==i,])>10 ){
     temp= all.markers_alo[all.markers_alo$cluster==i,"gene"][1:6]
      top_features_alo<-c(top_features_alo,temp)
  }else {
    temp= all.markers_alo[all.markers_alo$cluster==i,"gene"][1:nrow(all.markers_alo[all.markers_alo$cluster==i,])]
      top_features_alo<-c(top_features_alo,temp)
    
  }


}


DoHeatmap(alo_combined.sct,group.by = "ident",features =top_features_alo)+ scale_fill_viridis()
```

### Cell type identification

#### Single R (automated assignement)

```{r setup alo, include=FALSE, message=FALSE }

pred.alo_mouse <- SingleR(test = as.SingleCellExperiment(alo_combined.sct), ref = Mrna_ref, assay.type.test=1,
    labels = Mrna_ref$label.main,clusters = Idents(alo_combined.sct),de.method="wilcox")

for (i in 1:nrow(pred.alo_mouse)){
  if(pred.alo_mouse$tuning.scores$second[i]>0.1){
    pred.alo_mouse$labels[i]<-pred.alo_mouse$labels[i]
  } else { pred.alo_mouse$labels[i]<-"NA"
  }
}



# score.alo_mouse<-pruneScores(pred.alo_mouse,nmads=2,min.diff.med=0.1)
# for (i in 1:nrow(pred.alo_mouse)){
#   if(score.alo_mouse[i]==FALSE){
#     pred.alo_mouse$labels[i]<-pred.alo_mouse$labels[i]
#   } else { pred.alo_mouse$labels[i]<-"NA"
#   }
# }

  new_id_clusters=Idents(alo_combined.sct)
for (i in 1:nrow(pred.alo_mouse)){
  new_id_clusters<-str_replace_all(new_id_clusters, rownames(pred.alo_mouse)[i], pred.alo_mouse$labels[i]) 
}


alo_combined.sct@meta.data$singler_mouse<-new_id_clusters
```



```{r setup alo im , include=FALSE, message=FALSE}


pred.alo_im <- SingleR(test = as.SingleCellExperiment(alo_combined.sct), ref = Mim_ref, assay.type.test=1,
    labels = Mim_ref$label.main,clusters = Idents(alo_combined.sct),de.method="wilcox")
score.alo_im<-pruneScores(pred.alo_im,nmads=2,min.diff.med=0.1)

for (i in 1:nrow(pred.alo_im)){
  if(pred.alo_im$tuning.scores$second[i]>0.1){
    pred.alo_im$labels[i]<-pred.alo_im$labels[i]
  } else { pred.alo_im$labels[i]<-"NA"
  }
}



# for (i in 1:nrow(pred.alo_im)){
#   if(score.alo_im[i]==FALSE){
#     pred.alo_im$labels[i]<-pred.alo_im$labels[i]
#   } else { pred.alo_im$labels[i]<-"NA"
#   }
# }


  new_id_clusters=Idents(alo_combined.sct)
for (i in 1:nrow(pred.alo_im)){
  new_id_clusters<-str_replace_all(new_id_clusters, rownames(pred.alo_im)[i], pred.alo_im$labels[i]) 
}


alo_combined.sct@meta.data$singler_im<-new_id_clusters

```

```{r, include=FALSE, message=FALSE }
p_mouse<-DimPlot(alo_combined.sct, reduction = "umap", group.by = "singler_mouse")
p_im<-DimPlot(alo_combined.sct, reduction = "umap", group.by = "singler_im")

plot_grid( p3,p_mouse,p_im)
plot_grid( p3,p_mouse)
```

### Adipocyte differenciation markers

```{r feature plot markers adipo, echo=FALSE}
FeaturePlot(alo_combined.sct, features = c("Pparg","Igf1","Tgfbi","Tgfb3","Sparc","Angptl4","Pex5l"), pt.size = 0.3, 
    ncol = 3)
```

### Pseudo-time analosis

```{r, echo=FALSE, message=FALSE, warning=FALSE }
alo_combined.sct.cds <- as.cell_data_set(alo_combined.sct)
alo_combined.sct.cds<- cluster_cells(cds = alo_combined.sct.cds, reduction_method = "UMAP",resolution = 0.005)

alo_combined.sct.cds <- learn_graph(alo_combined.sct.cds, use_partition = TRUE)

plot_cells(alo_combined.sct.cds,
           color_cells_by = "cluster",
           label_groups_by_cluster=FALSE,
           label_leaves=TRUE,
           label_branch_points=TRUE)

alo_combined.sct.cds <- order_cells(alo_combined.sct.cds, root_pr_nodes=get_earliest_principal_node(alo_combined.sct.cds,3),reduction_method = "UMAP")
plot_cells(
  cds = alo_combined.sct.cds,
  color_cells_by = "pseudotime",
  show_trajectory_graph = TRUE
)
```

### Cell type Identification
 
 - 0 : Mature adipocyte
 - 1 : Macrophage 
 - 2 : Fibroblast ( pre-adipocyte)
 - 3 : Natural killer
 - 4 : Fibroblast 
 - 5 : Pre adipocyte (adamtsl1)
 - 6 : Unknown (Dao)
 - 7 : Neutrophils
 - 8 : Macrophages
 - 9 : Endothelial cell

```{r alo cell type id, echo=FALSE}
#Cell_types= c("Mature adipocyte","Pre-adipocyte 1 (Tshz2)", "Macrophage", "Precursor (Dao)", "Mature adipocyte (acaca)", "Endothelial cell", "Muscle cell", "Neutrophil", "Natural killer", "Pre-adipocyte 2 (adamtsl1)", "Lymphocyte","Undefined")

new.cluster.ids <- c("Mature adipocyte", "Macrophage","Pre-adipocyte 1 (Tshz2)","Natural killer","Pre-adipocyte 1 (Tshz2)","Pre-adipocyte 2 (adamtsl1)","Precursor (Dao)","Neutrophil","Dendritic cell","Endothelial cell")

names(new.cluster.ids) <- levels(alo_combined.sct)
alo_combined.sct<- RenameIdents(alo_combined.sct, new.cluster.ids)

pal=as.vector(Colours[match(levels(alo_combined.sct),Colours$Cell_types),2])
p_alo_combined.sct<-DimPlot(alo_combined.sct, reduction = "umap",  pt.size = 0.4,repel = TRUE, cols=pal ) 
p_alo_combined.sct

```

***

## DR old 1 (72)

```{r load dro_72,message=FALSE,warning=FALSE, echo = FALSE}
dro_72.data <- Read10X(data.dir = "/Users/njaure/Documents/Main_thesis_project/10X_full_experiment_10.20/comp_data_10.20/72_dro//A006200124_136872_S10_L00Solo.out/GeneFull/raw/")
dro_72 <- CreateSeuratObject(counts = dro_72.data, project = "dr_old_1", min.cells = 10, min.features = 80)
dro_72@meta.data$batch <- "batch_2"
dro_72@meta.data$diet <- "DR"
dro_72@meta.data$age <- "old"
dro_72
```

- 5264 features across 1517 samples after first filtering of taking features across minimum 10 cells, and cells minimum 80 features. 

### Quality assessment

```{r plot quality dro, echo = FALSE}
dro_72[["percent.rp"]] <- PercentageFeatureSet(dro_72, pattern = "^Rp")
dro_72[["percent.mt"]] <- PercentageFeatureSet(dro_72, pattern = "^mt-")
VlnPlot(dro_72, features = c("nFeature_RNA", "nCount_RNA","percent.mt","percent.rp"), ncol = 4)

```

```{r plot quality 2 dro,echo = FALSE}
FeatureScatter(dro_72, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

```

- no big abnormality detected, filtering on 50<x<220,mt<2, rp<1

```{r filtering2 dro, message=FALSE, warning=FALSE,echo = FALSE}
dro_72 <- subset(dro_72, subset = nFeature_RNA > 50 & nFeature_RNA < 500 & nCount_RNA < 1000 & percent.mt < 2 & percent.rp < 1)

```

- 5264 features across 1437 samples after second filtering. 

### Normalisation

```{r sctransform dro,message=FALSE, warning=FALSE}
# run sctransform
dro_72 <- SCTransform(dro_72, vars.to.regress = c("percent.mt","percent.rp"), verbose = FALSE)
dro_72
```


***

## DR old 2 (07)

```{r load dro_07,message=FALSE,warning=FALSE, echo = FALSE}
dro2_07.data <- Read10X(data.dir = "/Users/njaure/Documents/Main_thesis_project/10X_full_experiment_10.20/comp_data_10.20/07_dro2/A006200124_137507_S12_L00Solo.out/GeneFull/raw/")

dro2_07 <- CreateSeuratObject(counts = dro2_07.data, project = "dr_old_2", min.cells = 5, min.features = 80)
dro2_07@meta.data$batch <- "batch_3"
dro2_07@meta.data$diet <- "DR"
dro2_07@meta.data$age <- "old"
dro2_07
```

- 1512 features across 348 samples after first filtering of taking features across minimum 5 cells, and cells minimum 80 features. 

### Quality assessment

```{r plot quality dro 2, echo = FALSE}
dro2_07[["percent.rp"]] <- PercentageFeatureSet(dro2_07, pattern = "^Rp")
dro2_07[["percent.mt"]] <- PercentageFeatureSet(dro2_07, pattern = "^mt-")
VlnPlot(dro2_07, features = c("nFeature_RNA", "nCount_RNA","percent.mt","percent.rp"), ncol = 4)

```

```{r plot quality 2 dro 2,echo = FALSE}
FeatureScatter(dro2_07, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

```

- no big abnormality detected, filtering on 50<x<220,mt<2, rp<1

```{r filtering2 dro 2, message=FALSE, warning=FALSE,echo = FALSE}
dro2_07 <- subset(dro2_07, subset = nFeature_RNA > 50 & nFeature_RNA < 500 & nCount_RNA < 300 & percent.mt < 2 & percent.rp < 1)

```

- 1512 features across 288 samples after second filtering. 

### Normalisation

```{r sctransform dro 2,message=FALSE, warning=FALSE}
# run sctransform
dro2_07 <- SCTransform(dro2_07, vars.to.regress = c("percent.mt","percent.rp"), verbose = FALSE)
dro2_07
```


***
<br>
***

### Merging

```{r merging dro,message=FALSE, warning=FALSE, echo = FALSE}
dro_data<-list(dro_72,dro2_07)
dro_features <- SelectIntegrationFeatures(object.list = dro_data, nfeatures = 5000)
dro_list <- PrepSCTIntegration(object.list = dro_data, anchor.features = dro_features, 
    verbose = FALSE)
dro_anchors <- FindIntegrationAnchors(object.list = dro_list, normalization.method = "SCT", 
    anchor.features = dro_features)
dro_combined.sct <- IntegrateData(anchorset = dro_anchors, normalization.method = "SCT")

dro_combined.sct <- RunPCA(dro_combined.sct, verbose = FALSE)
dro_combined.sct <- RunUMAP(dro_combined.sct, reduction = "pca", dims = 1:30)
```

- 12096 features across 1725 samples after merging.

```{r}
dim(dro_combined.sct)
```


```{r umap plot dro, echo = FALSE}
p1<-DimPlot(dro_combined.sct, reduction = "umap", group.by = "orig.ident")
p1
```

### Clustering

```{r clustering dro, echo = FALSE}
dro_combined.sct <- FindNeighbors(dro_combined.sct, reduction = "pca", dims = 1:30)
dro_combined.sct <- FindClusters(dro_combined.sct, resolution = 0.6)
p3 <- DimPlot(dro_combined.sct, reduction = "umap")
plot_grid( p1,p3)
```

```{r umap per quality criteria dro, echo = FALSE}
FeaturePlot(dro_combined.sct,features = c("nFeature_RNA", "nCount_RNA","percent.mt","percent.rp"))
FeaturePlot(dro_combined.sct,features = c("Mecom", "Dao","Stab2","Cd105"))
```

### Gene Markers


```{r}
dro_combined.sct
DefaultAssay(dro_combined.sct)<-"SCT"
dim(dro_combined.sct)
```

```{r topmarker dro, echo = FALSE, warning=FALSE, message=FALSE}
all.markers_dro=FindAllMarkers(dro_combined.sct,only.pos = TRUE, min.pct = 0.2, logfc.threshold = 0.2,min.cells.feature = 50,test.use = "t")

top_features_dro=vector()
temp=vector()
for ( i in 0:length(unique(all.markers_dro$cluster))){
  if (nrow(all.markers_dro[all.markers_dro$cluster==i,])>10 ){
     temp= all.markers_dro[all.markers_dro$cluster==i,"gene"][1:2]
      top_features_dro<-c(top_features_dro,temp)
  }else {
    temp= all.markers_dro[all.markers_dro$cluster==i,"gene"][1:2]
      top_features_dro<-c(top_features_dro,temp)
    
  }


}

VlnPlot(dro_combined.sct, features = top_features_dro, 
    pt.size = 0.2, stack = TRUE)


```

```{r feature plot dro, echo = FALSE, warning=FALSE}
FeaturePlot(dro_combined.sct, features = top_features_dro, pt.size = 0.2, 
    ncol = 3)
```


```{r heatmap dro, echo = FALSE, warning=FALSE, message=FALSE}

top_features_dro=vector()
temp=vector()
for ( i in 0:length(unique(all.markers_dro$cluster))){
  if (nrow(all.markers_dro[all.markers_dro$cluster==i,])>10 ){
     temp= all.markers_dro[all.markers_dro$cluster==i,"gene"][1:6]
      top_features_dro<-c(top_features_dro,temp)
  }else {
    temp= all.markers_dro[all.markers_dro$cluster==i,"gene"][1:nrow(all.markers_dro[all.markers_dro$cluster==i,])]
      top_features_dro<-c(top_features_dro,temp)
    
  }


}


DoHeatmap(dro_combined.sct,group.by = "ident",features =top_features_dro)+ scale_fill_viridis()
```

### Cell type identification

#### Single R (automated assignement)

```{r setup dro, include=FALSE, message=FALSE }

pred.dro_mouse <- SingleR(test = as.SingleCellExperiment(dro_combined.sct), ref = Mrna_ref, assay.type.test=1,
    labels = Mrna_ref$label.main,clusters = Idents(dro_combined.sct),de.method="wilcox")

score.dro_mouse<-pruneScores(pred.dro_mouse,nmads=2,min.diff.med=0.2)
for (i in 1:nrow(pred.dro_mouse)){
  if(score.dro_mouse[i]==FALSE){
    pred.dro_mouse$labels[i]<-pred.dro_mouse$labels[i]
  } else { pred.dro_mouse$labels[i]<-"NA"
  }
}

  new_id_clusters=Idents(dro_combined.sct)
for (i in 1:nrow(pred.dro_mouse)){
  new_id_clusters<-str_replace_all(new_id_clusters, rownames(pred.dro_mouse)[i], pred.dro_mouse$labels[i]) 
}


dro_combined.sct@meta.data$singler_mouse<-new_id_clusters
```



```{r setup dro im , include=FALSE, message=FALSE}


pred.dro_im <- SingleR(test = as.SingleCellExperiment(dro_combined.sct), ref = Mim_ref, assay.type.test=1,
    labels = Mim_ref$label.main,clusters = Idents(dro_combined.sct),de.method="wilcox")
score.dro_im<-pruneScores(pred.dro_im,nmads=2,min.diff.med=0.1)

for (i in 1:nrow(pred.dro_im)){
  if(score.dro_im[i]==FALSE){
    pred.dro_im$labels[i]<-pred.dro_im$labels[i]
  } else { pred.dro_im$labels[i]<-"NA"
  }
}


  new_id_clusters=Idents(dro_combined.sct)
for (i in 1:nrow(pred.dro_im)){
  new_id_clusters<-str_replace_all(new_id_clusters, rownames(pred.dro_im)[i], pred.dro_im$labels[i]) 
}


dro_combined.sct@meta.data$singler_im<-new_id_clusters

```

```{r, include=FALSE, message=FALSE }
p_mouse<-DimPlot(dro_combined.sct, reduction = "umap", group.by = "singler_mouse")
p_im<-DimPlot(dro_combined.sct, reduction = "umap", group.by = "singler_im")

plot_grid( p3,p_mouse,p_im)

```

### Adipocyte differenciation markers

```{r feature plot markers adipo dro, echo=FALSE}
FeaturePlot(dro_combined.sct, features = c("Pparg","Igf1","Tgfbi","Tgfb3","Sparc","Angptl4","Pex5l"), pt.size = 0.3, 
    ncol = 3)
```

### Pseudo-time androsis

```{r, echo=FALSE, message=FALSE, warning=FALSE }
dro_combined.sct.cds <- as.cell_data_set(dro_combined.sct)
dro_combined.sct.cds<- cluster_cells(cds = dro_combined.sct.cds, reduction_method = "UMAP",resolution = 0.005)

dro_combined.sct.cds <- learn_graph(dro_combined.sct.cds, use_partition = TRUE)

plot_cells(dro_combined.sct.cds,
           color_cells_by = "cluster",
           label_groups_by_cluster=FALSE,
           label_leaves=TRUE,
           label_branch_points=TRUE)

dro_combined.sct.cds <- order_cells(dro_combined.sct.cds, root_pr_nodes=get_earliest_principal_node(dro_combined.sct.cds,2),reduction_method = "UMAP")
plot_cells(
  cds = dro_combined.sct.cds,
  color_cells_by = "pseudotime",
  show_trajectory_graph = TRUE
)
```

### Cell type Identification
 
 - 0 : Fibroblast ( pre-adipocyte)
 - 1 : Mature adipocytes
 - 2 : Unknown (Dao)
 - 3 : Macrophages
 - 4 : Endothelial cell ?


```{r dro cell type id, echo=FALSE}
#Cell_types= c("Mature adipocyte","Pre-adipocyte 1 (Tshz2)", "Macrophage", "Precursor (Dao)", "Mature adipocyte (acaca)", "Endothelial cell", "Muscle cell", "Neutrophil", "Natural killer", "Pre-adipocyte 2 (adamtsl1)", "Lymphocyte","Undefined")

new.cluster.ids <- c("Pre-adipocyte 1 (Tshz2)","Mature adipocyte","Precursor (Dao)", "Macrophage","Endothelial cell")

names(new.cluster.ids) <- levels(dro_combined.sct)
dro_combined.sct<- RenameIdents(dro_combined.sct, new.cluster.ids)

pal=as.vector(Colours[match(levels(dro_combined.sct),Colours$Cell_types),2])
p_dro_combined.sct<-DimPlot(dro_combined.sct, reduction = "umap",cols=pal, pt.size = 0.5,repel = TRUE ) 
p_dro_combined.sct

```

***

## Compare tissues



```{r merging o,message=FALSE, warning=FALSE, echo = FALSE}

DefaultAssay(dro_combined.sct)<-"RNA"
DefaultAssay(alo_combined.sct)<-"RNA"
o_data<-list(alo_71,alo2_06,dro_72)
o_features <- SelectIntegrationFeatures(object.list = o_data, nfeatures = 5000)
o_list <- PrepSCTIntegration(object.list = o_data, anchor.features = o_features, 
    verbose = FALSE)
o_anchors <- FindIntegrationAnchors(object.list = o_list, normalization.method = "SCT", 
    anchor.features = o_features)
o_combined.sct <- IntegrateData(anchorset = o_anchors, normalization.method = "SCT")

o_combined.sct <- RunPCA(o_combined.sct, verbose = FALSE)
o_combined.sct <- RunUMAP(o_combined.sct, reduction = "pca", dims = 1:30)
```

- 12096 features across 1725 samples after merging.

```{r}
dim(o_combined.sct)
```


```{r umap plot o, echo = FALSE}
p1<-DimPlot(o_combined.sct, reduction = "umap", group.by = "orig.ident")
p1
DimPlot(o_combined.sct, reduction = "umap", split.by = "diet" )
```